Towards a Complete Model of the Negative Selection Process in Humans

### 2023-06-21 manuscript/manuscript.tex
ms changes

The continual influx of new mutations into populations is the ultimate source
of all adaptations, but the vast majority of mutations either do not affect
fitness or are deleterious. Negative selection works to eliminate such
deleterious mutations from the population, which is essential to maintaining
the integrity of information in the genome to maintain a lineage. Mutations
under negative selection are kept at low frequencies (Haldane?), contributing
to human traits (XXX) and diseases. As with most selection in the genome, this
process perturbs the allele frequencies of neighboring linked variation. This
reduces genetic variability around conserved segments and creates large-scale
spatial patterns in genetic diversity. These patterns are mediated by the
deleterious mutation rate, the strength of selection in conserved segments, and
the spatial distribution of recombination rates and conserved segments. Since
genome-wide recombination maps and putatively conserved segments are available
for many species, researchers have combined these with population genetic
theory to estimate the mutation rate and selection coefficients of deleterious
mutations, as well as the overall reduction in genetic variability due to the
negative selection process.

@@

\subsection*{Predicted Diversity and $B'(x)$ maps}

@@

First, the split time between humans and chimpanzees is unknown, with estimates
ranging from 6Mya to 12Mya (XXX). Second, our predictions are in sites per
generation, and the appropriate human generation time is unknown. Third,

>>>>

The continual influx of new mutations into populations is the ultimate source
of all adaptations, but the vast majority of mutations either do not affect
fitness or are deleterious. Negative selection works to eliminate such
deleterious mutations from the population, which is essential to maintaining
the integrity of information in the genome needed to maintain a lineage.
Mutations under negative selection are kept at low frequencies (Haldane?),
contributing to human traits (XXX) and diseases. As with most selection in the
genome, this process perturbs the allele frequencies of neighboring linked
variation. This reduces genetic variability around conserved segments and
creates large-scale spatial ``linked selection signal" in genetic diversity.
Mutation and negative selection's contribution to this signal is mediated by
the deleterious mutation rate, the strength of selection in conserved segments,
and the spatial distribution of recombination rates and conserved segments.
Since genome-wide recombination maps and putatively conserved segments are
available for many species, researchers have combined these with population
genetic theory to estimate the mutation rate and selection coefficients of
deleterious mutations, as well as the overall reduction in genetic variability
due to the negative selection process.

@@

\subsection*{Predicted Diversity Substitution Rates}

\begin{figure}[htbp] \centering
    \includegraphics[width=\textwidth]{figures/figure_4.pdf} 
    \caption{}
  \label{fig:figure-4}
\end{figure}

@@

First, the split time between humans and chimpanzees is unknown, with estimates
ranging from 6Mya to 12Mya (XXX). Second, our predictions are in sites per
generation, and the appropriate human generation time is unknown. Third, the
appropriate mutation rate to use is debated, since there may have been a
mutational slow down on the human lineage (XXX), which could explain why
phylogenetic- and pedigree-based mutation rate estimates differ by roughly a
factor of two (XXX). Finally, we are only considering modeling the deleterious
substitution rate. In reality, some fraction of observed substitutions fixed
because they were beneficial.
